Augmentation of a Historical Harpsichord Keyboard Replica for Haptic-Enabled Interaction in Museum Exhibitions

### 2025-01-25 src/main.tex
move Ethical Standards

%%
%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acks}
This work received funding from the European Commission's Horizon2020 programme, through grant ERC-StG 950084 NEMUS. We acknowledge the invaluable contributions of
\begin{itemize}
\item
  Università di Bologna
  \begin{itemize}
  \item
    Alma Labor
    \begin{itemize}
    \item
      Massimiliano Fraulini and the staff of Alma Labor at the Università
      di Bologna for their 3D printing expertise and generosity with
      electronics equipment
    \end{itemize}
  \item
    Fisica Tecnica
    \begin{itemize}
    \item
      Maurzio Chendi Fabrizio Casarini, Giulio Severo and Barbara
      Costantini
    \end{itemize}
  \end{itemize}
\item
  Edinburgh
  \begin{itemize}
  \item
    uCreate
    \begin{itemize}    
    \item
      Simeon, Stuart, Millie, and Ruth of uCreate at the Univeristy of
      Edinburgh for their support with soldering facilities.
    \end{itemize}
  \item
    University of Edinburgh
    \begin{itemize}
    \item
      Richard Collins and the Digital Making Staff at the Edinburgh
      College of Art for 3D printing instruction and CNC support.
    \item
      Joe Hathaway of Digital Development at the College of Art for
      providing electronics components
    \item
      St Cecilia's Jenny Nex
    \end{itemize}
  \end{itemize}
\end{itemize}

@@

>>>>

%%
%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.

\begin{acks}
 We acknowledge the invaluable contributions of
\begin{itemize}
\item
  Università di Bologna
  \begin{itemize}
  \item
    Alma Labor
    \begin{itemize}
    \item
      Massimiliano Fraulini and the staff of Alma Labor at the Università
      di Bologna for their 3D printing expertise and generosity with
      electronics equipment
    \end{itemize}
  \item
    Fisica Tecnica
    \begin{itemize}
    \item
      Maurzio Chendi Fabrizio Casarini, Giulio Severo and Barbara
      Costantini
    \end{itemize}
  \end{itemize}
\item
  Edinburgh
  \begin{itemize}
  \item
    uCreate
    \begin{itemize}    
    \item
      Simeon, Stuart, Millie, and Ruth of uCreate at the Univeristy of
      Edinburgh for their support with soldering facilities.
    \end{itemize}
  \item
    University of Edinburgh
    \begin{itemize}
    \item
      Richard Collins and the Digital Making Staff at the Edinburgh
      College of Art for 3D printing instruction and CNC support.
    \item
      Joe Hathaway of Digital Development at the College of Art for
      providing electronics components
    \item
      St Cecilia's Jenny Nex
    \end{itemize}
  \end{itemize}
\end{itemize}

@@

\section{Ethical Standards}
This work received funding from the European Commission's Horizon2020 programme, through grant \anon{ERC-StG 950084 NEMUS}
